My title

### 2024-11-22 paper/paper.qmd
update paper

@@

```{r}
#| label: fig-corr-temp
#| fig-cap: Temperature Values Have High Correlations
#| fig-subcap: ['High Correlations Between Max, Min and Mean Temperature', 'Other Predictors Does Not Have High Correlations', 'Linear Relationship Between Max and Mean Temperature', 'Linear Relationship Between Min and Mean Temperature']
#| echo: false
#| warning: false
#| layout-ncol: 2
selected_data_0 <- analysis_data[, c("wind_speed", "pressure_station", "snow",  "min_temp", "log_mean_temp", 'max_temp', "total_rain", "gust_speed_km_h")]
colnames(selected_data_0) <- c("Wind Speed (km/h)", "Station Pressure (hPa)", "Snow (cm)", 
                               "Min Temperature (°C)", "Log Mean Temperature (°F)", 
                               "Max Temperature (°C)", "Total Rain (mm)", 
                               "Gust Speed (km/h)")

@@

selected_data_1 <- analysis_data[, c("wind_speed", "pressure_station", "snow", "log_mean_temp", "total_rain", "gust_speed_km_h")]
colnames(selected_data_1) <- c("Wind Speed (km/h)", "Station Pressure (hPa)", "Snow (cm)", 
                               "Log Mean Temperature (°F)", "Total Rain (mm)", 
                               "Gust Speed (km/h)")

>>>>

```{r}
# Calculate diagnostic measures
glm_model <- glm
# Assuming `glm_model` is your fitted model

# 1. Linearity: Residuals vs Fitted Plot
plot(glm_model, which = 1, main = "Linearity Check: Residuals vs Fitted")
# Look for a random scatter of points. Patterns indicate non-linearity.

# 2. Homoscedasticity: Scale-Location Plot
plot(glm_model, which = 3, main = "Homoscedasticity Check: Scale-Location")
# Points should be evenly spread. A funnel shape indicates heteroscedasticity.

# 3. Normality of Residuals: Q-Q Plot
plot(glm_model, which = 2, main = "Normality Check: Q-Q Plot")
# Points should lie approximately along the diagonal line.

# 4. Residual Histogram: Another Normality Check
residuals <- residuals(glm_model)
hist(residuals, main = "Histogram of Residuals", xlab = "Residuals")
# Check for symmetry. A skewed histogram suggests non-normal residuals.

# 5. Multicollinearity: Variance Inflation Factor (VIF)
library(car)
vif_values <- vif(glm_model)
print(vif_values)
# VIF > 5 indicates high multicollinearity. Consider removing highly correlated predictors.

# 6. Cook's Distance: Influence of Observations
cooksd <- cooks.distance(glm_model)
plot(cooksd, main = "Cook's Distance", type = "h")
abline(h = 4 / nrow(model.frame(glm_model)), col = "red", lty = 2)
# Points above the red line are highly influential.

# 7. Leverage: Identify High Leverage Points
leverage <- hatvalues(glm_model)
plot(leverage, main = "Leverage Check", type = "h")
abline(h = 2 * mean(leverage), col = "red", lty = 2)
# Points above the red line have high leverage.

# 8. Correlation Between Predictors
cor_matrix <- cor(model.frame(glm_model)[, -1]) # Exclude response variable
print(round(cor_matrix, 2))
# Check for highly correlated predictors (e.g., correlation > 0.8 or < -0.8).

@@

```{r}
#| label: fig-corr-temp
#| fig-cap: Temperature Values Have High Correlations
#| fig-subcap: ['High Correlations Between Max, Min and Mean Temperature, Total Precip and Rain', 'Other Predictors Does Not Have High Correlations', 'Linear Relationship Between Max and Mean Temperature', 'Linear Relationship Between Min and Mean Temperature']
#| echo: false
#| warning: false
#| layout-ncol: 2
selected_data_0 <- analysis_data[, c("wind_speed", "pressure_station", "snow",  "min_temp", "log_mean_temp", 'max_temp', "total_rain", "gust_speed_km_h", 'total_precipitation')]
colnames(selected_data_0) <- c("Wind Speed (km/h)", "Station Pressure (hPa)", "Snow (cm)", 
                               "Min Temperature (°C)", "Log Mean Temperature (°F)", 
                               "Max Temperature (°C)", "Total Rain (mm)", 
                               "Gust Speed (km/h)", "Total Precipitation (mm)")

@@

selected_data_1 <- analysis_data[, c("wind_speed", "pressure_station", "snow", "log_mean_temp", "total_precipitation", "gust_speed_km_h")]
colnames(selected_data_1) <- c("Wind Speed (km/h)", "Station Pressure (hPa)", "Snow (cm)", 
                               "Log Mean Temperature (°F)", "Total Precip (mm)", 
                               "Gust Speed (km/h)")
